non_phylo_analyses

### 2018-04-09 reports/non_phylo_model.Rmd
looking at VIF and also model selection via best subset selection

completely naive model, plant eater taken out cause it only had one level.

@@

naive_mod<-lm(log(urban_median)~log(mean_body_size)+log(clutch_size)+iucn_status+feeding_habitat_generalism+Habitat_agricultural+Habitat_grass_shrubland+Habitat_tree_forest+breeding_habitat_generalism+granivore+insectivore+carrion_eater+diet_generalism+plant_eater+movement_class+ground_nesting+hollow_nesting+nest_generalism+breeding+nest_aggregation+feeding_aggregation,data=df2,na.action = "na.fail", weights=(df2$N/df2$unique_localities))
summary(naive_mod)
dim(df2)
```

@@

```{r}
anova(naive_mod)
```
and some not-so-quick model selection.  dredge takes a little while because it considers all combinations of predictor variables.

@@

>>>>

@@

naive_mod<-lm(log(urban_median)~log(mean_body_size)+log(clutch_size)+iucn_status+feeding_habitat_generalism+brain_residual+Habitat_agricultural+Habitat_grass_shrubland+Habitat_tree_forest+breeding_habitat_generalism+granivore+insectivore+carrion_eater+diet_generalism+plant_eater+movement_class+ground_nesting+hollow_nesting+nest_generalism+breeding+nest_aggregation+feeding_aggregation,data=df2,na.action = "na.fail", weights=(df2$N/df2$unique_localities))
summary(naive_mod)
dim(df2)
```

@@

```{r}
anova(naive_mod)
```

checking for multicolinearity
```{r}
library(car)
vif()
```

and some not-so-quick model selection.  dredge takes a little while because it considers all combinations of predictor variables.

@@

another type of potential model selection

```{r}
library(leaps)

model_all_select <- regsubsets(log(urban_median)~log(mean_body_size)+log(clutch_size)+iucn_status+feeding_habitat_generalism+brain_residual+Habitat_agricultural+Habitat_grass_shrubland+Habitat_tree_forest+breeding_habitat_generalism+granivore+insectivore+carrion_eater+diet_generalism+plant_eater+movement_class+ground_nesting+hollow_nesting+nest_generalism+breeding+nest_aggregation+feeding_aggregation,data=df2,na.action = "na.fail", weights=(df2$N/df2$unique_localities), method = "exhaustive")

results <- summary(model_all_select)

which.max(results$adjr2)

which.min(results$bic)

which.min(results$cp)
